An Empirical Analysis of the Role of Energy in Economic Growth

### 2014-05-04 Article/EconGrowth2.Rnw
Linex graphs now working in the paper.

\twocolumn{}
<<LINEXq_Resample_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7, fig.cap="LINEX model (with energy) resampling results.">>=
linexCoeffsData <- loadResampledData(archive=archive, 
                                     country=countryAbbrevs, 
                                     model="linex", 
                                     factors=c("iK+iL+iQ"), 
                                     kind="coeffs")
# Rearrange the country factors to obtain our preferred ordering.
linexCoeffsData$country <- as.factor(linexCoeffsData$country)
for (lev in rev(countryAbbrevs)) { linexCoeffsData$country <- relevel(linexCoeffsData$country, ref=lev) }

standardScatterPlot(data=linexCoeffsData, aes(a_0, c_t), facet_formula=country~energy, alpha=0.05) +
    labs(x=expression(a[0]), y=expression(c[t])) +
     scale_x_continuous(limits=c(-1, 2), breaks=c(-1, 0, 1.0, 2.0)) +
     scale_y_continuous(limits=c(0, 10), breaks=c(0, 5, 10))
@

<<LINEX_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7.1, fig.cap="LINEX fitted models.">>=
linexFittedData <- loadResampledData(archive=archive, 
                                     country=countryAbbrevs, 
                                     model="linex",
                                     factors=c("iK+iL+iQ"), 
                                     kind="fitted")

spaghettiPlot(data=linexFittedData, facet_formula=Country ~ Energy, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1980=1 or 1991=1)")
@
\onecolumn{}

>>>>

\twocolumn{}
<<LINEXq_Resample_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7, fig.cap="LINEX model (with energy) resampling results.">>=
linexCoeffsData <- filter(coef_df, model=="linex", energy=="iQ")
# Rearrange the country factors to obtain our preferred ordering.
linexCoeffsData$country <- as.factor(linexCoeffsData$country)
for (lev in rev(countryAbbrevs)) { linexCoeffsData$country <- relevel(linexCoeffsData$country, ref=lev) }
standardScatterPlot(data=linexCoeffsData, aes(a_0, c_t), facet_formula=country~energy, alpha=0.05) +
    labs(x=expression(a[0]), y=expression(c[t])) +
     scale_x_continuous(limits=c(-1, 2), breaks=c(-1, 0, 1.0, 2.0)) +
     scale_y_continuous(limits=c(0, 10), breaks=c(0, 5, 10))
@

<<LINEX_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7.1, fig.cap="LINEX fitted models.">>=
# linexFittedData <- loadResampledData(archive=archive, 
#                                      country=countryAbbrevs, 
#                                      model="linex",
#                                      factors=c("iK+iL+iQ"), 
#                                      kind="fitted")

linexFittedData <- filter(fitted_df, model=="linex", energy=="iQ")
spaghettiPlot(data=linexFittedData, facet_formula=Country~energy, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1980=1 or 1991=1)")
@
\onecolumn{}
